Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-05 paper/paper.tex
update

>>>>

\hy{I found this section confusing in the following sense. First,
it does not highlight the most interesting aspects of the compilation
of Anglican. It gives a good overview on how the compilation is
implemented, but a reader might want to see something unique and
interesting about Anglican. To me, the most interesting part of the
compilation is the treatment of probabilistic constructs in Anglican's
CPS transformation. How are sample,
observe and stochastic memoization compiled? How should the standard
CPS transformation be modified in order to handle these constructs?
The use of state can be one answer for the second question.
The second most interesting part is about the use of trampolining
the mix with Clojure code.

Second, the section assumes that a reader is already familiar 
with Clojure or something specific to probabilistic programming. For 
instance, it might be that a reader  has never heard about
Clojure records and stochastic memoization. Then, she or he
would have difficulties in following this section.

What should we do? One option is not to do anything. Another is
to take care of the second point. That is, we make the section
easily followed by someone who does not know Clojure. The third
is to restructure the section and to take care of my first criticism.}
